|

### 2025-01-31 doc/paper.qmd
new

**Step 2: Data Preparation**  
The merged dataset would integrate stock return data from CRSP (`crsp_daily_stock_returns`), firm fundamentals from Compustat (`compustat_fundq_1972_2023`), and the CRSP-Compustat linking table (`linkdata_compustat_crsp.parquet`). The `PERMNO` identifier from CRSP and `GVKEY` from Compustat are connected via `LPERMNO` in the linking table, ensuring correct firm-year alignment. Unnecessary variables from linked table, such as `linkprim`, `liid`, `linktype`, and `usedflag`, are dropped. The resulting dataset would retain only daily stock returns (`ret`), earnings announcement dates (`rdq`), fiscal year-end indicators (`fyr`), and firm identifiers (`permno, gvkey`), used further for BHR calculation and regression analysis.

After defining the event windows for each earnings announcement day in Q1-Q4, retain only the firms that have four earnings announcements per year, such that each of them falls within the same calendar year. Additionally, for the subgroup replication of Table 2 Panels C-D classify the firms based on their fiscal year-end (`fyr`) to define whether firms have December fiscal year-end firm or in any another month.

**Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data. The analysis begins by calculating the market shares of the Big 4, 10KAP, and CR4 audit firm groups for the number of statutory audits conducted in 2021. For each country, the Big 4 market share is derived as the percentage of PIE statutory audits conducted by Deloitte, EY, KPMG, and PwC, while the CR4 market share represents the top four audit firms in each country based on audit counts. The 10KAP market share includes the Big 4 along with six additional networks, providing a broader view of market concentration.

@@

The following formula is used to calculate market share:
$$
\text{Market Share (\%)} = \left( \frac{\text{Number of PIE Audits by Network Group}}{\text{Total PIE Audits in Country}} \right) \times 100
$$

>>>>

**Step 2: Data Preparation**  
Although not finished, the plan would be as follows: The merged dataset would integrate stock return data from CRSP (`crsp_daily_stock_returns`), firm fundamentals from Compustat (`compustat_fundq_1972_2023`), and the CRSP-Compustat linking table (`linkdata_compustat_crsp.parquet`). The `PERMNO` identifier from CRSP and `GVKEY` from Compustat are connected via `LPERMNO` in the linking table, ensuring correct firm-year alignment. Unnecessary variables from linked table, such as `linkprim`, `liid`, `linktype`, and `usedflag`, are dropped. The resulting dataset would retain only daily stock returns (`ret`), earnings announcement dates (`rdq`), fiscal year-end indicators (`fyr`), and firm identifiers (`permno, gvkey`), used further for Buy-and-Hold Returns (BHR) calculation and regression analysis.

After defining the event windows for each earnings announcement day in Q1-Q4, retain only the firms that have four earnings announcements per year, such that each of them falls within the same calendar year. Additionally, for the subgroup replication of Table 2 Panels C-D classify the firms based on their fiscal year-end (`fyr`) to define whether firms have December fiscal year-end firm or in any another month. Control for the duplicate and missing firm/years.

**Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
The analysis step computes the BHR returns and performs a cross-sectional regression for each distinct firm/year.

@@

The following formula is used to calculate calendar-year buy-and-hold returns, that measures the stock’s total performance over the year for each firm using daily CRSP returns:
$$
BHR_{\text{annual}} = \prod_{t=1}^{T} (1 + R_t) - 1, \quad \text{where } R_t \text{ is the daily return and } T \text{ is the total trading days in a year.}
$$

Specifically, buy-and-hold return over the three-day event window, that measures the stock’s reaction only to earnings news, is computed as given below:
$$
BHR_{\text{annual}} = (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1, \quad \text{where } R_t \text{ is the daily return and } T \text{ is the total trading days in a year.}
$$

Next, perform cross-sectional regression for each firm/year - the main objective of @ball_how_2008's research:
$$
R_{\text{annual}} = \alpha_0 + \alpha_1 R_{\text{event}_1} + \alpha_2 R_{\text{event}_2} + \alpha_3 R_{\text{event}_3} + \alpha_4 R_{\text{event}_4} + \epsilon_i
$$

The DV (BHR_annual) is the firm’s calendar-year buy-and-hold return from CRSP, aggregated over all trading days, while the IVs (BHR_event) are the four quarterly earnings-announcement returns, computed as three-day buy-and-hold returns (-1, 0, +1) around each earnings announcement date (RDQ) from Compustat. Additionally, I compute abnormal  R^2 by benchmarking the adjusted  R^2  from annual regressions against the 4.8% baseline.
